Thesis Title

### 2022-03-16 chapters/introduction.tex
update figures

Despite the increasing adoption of DNA sequencing methods in clinical microbiology, the sequencing of genetic material from a pure culture requires \textit{a priori} knowledge of what to expect from a particular clinical sample or patient \citep{schuele_future_2021}. 
In most cases, this knowledge is enough to request the most appropriate test, such as multiplexed panels or specific culture media, but this is not always the case. 
In recent years, there has been a growing interest in using metagenomics to deliver culture-independent approaches to microbial ecology, surveillance and diagnosis \citep{loman_twenty_2015, loman_high-throughput_2012}.
Metagenomic DNA sequence allows detailed characterisation of pathogens in all kinds of samples originating from humans, animals, food and the environment, ligating the diagnostics to surveillance in a true "one health" fashion \citep{rossen__2018}. 
Unlike PCR or microarrays, it usually does not require primer or probe design, it can be easily multiplexed, and the specificity and selectivity of the sequencing can be adjusted computationally after acquiring the data \citep{dunne_next-generation_2012}.  
While most molecular assays target only a limited number of pathogens, metagenomic approaches characterise all DNA or RNA present in a sample, enabling analysis of the entire microbiome as well as the human host genome or transcriptome in patient samples \citep{chiu_clinical_2019}. 
Whether or not it can entirely replace routine microbiology depends on several conditions and future developments, both technological and computational (see \secref{sec:bioinformatics}).

\begin{figure*}[h!]
\centering
\includegraphics[width=\textwidth]{figures/introduction/Figure 4.pdf}
\caption{\textbf{Principles of current processing of bacterial pathogens based on whole genome sequencing.} Schematic representation of the workflow for processing samples for bacterial pathogens after adoption of whole genome sequencing, with an expected timescale that could fit within a single day. The culture steps would be the same as currently used in a routine microbiology laboratory. Once a likely pathogen is ready for sequencing, DNA will be extracted, taking as little as 2 hours to prepare the DNA for sequencing.
After sequencing, the main processes for yielding information will be computational. Automated sequence assembly algorithms are necessary for processing the raw sequence data, from which species, relationship to other isolates of the same species, antimicrobial resistance profile and virulence gene content can be assessed. All the results will also be used for outbreak detection and infectious diseases surveillance. Adapted from \cite{didelot_transforming_2012}}
\label{fig:figure3}
\end{figure*}

>>>>

Despite the increasing adoption of DNA sequencing methods in clinical microbiology, the sequencing of genetic material from a pure culture requires \textit{a priori} knowledge of what to expect from a particular clinical sample or patient \citep{schuele_future_2021}. 
In most cases, this knowledge is enough to request the most appropriate test, such as multiplexed panels or specific culture media, but this is not always the case. 
In recent years, there has been a growing interest in using metagenomics to deliver culture-independent approaches to microbial ecology, surveillance and diagnosis (see Figure \ref{fig:figure4})\citep{loman_twenty_2015, loman_high-throughput_2012}.
Metagenomic DNA sequence allows detailed characterisation of pathogens in all kinds of samples originating from humans, animals, food and the environment, ligating the diagnostics to surveillance in a true "one health" fashion \citep{rossen__2018}. 
Unlike PCR or microarrays, it usually does not require primer or probe design, it can be easily multiplexed, and the specificity and selectivity of the sequencing can be adjusted computationally after acquiring the data \citep{dunne_next-generation_2012}.  
While most molecular assays target only a limited number of pathogens, metagenomic approaches characterise all DNA or RNA present in a sample, enabling analysis of the entire microbiome as well as the human host genome or transcriptome in patient samples \citep{chiu_clinical_2019}. 
Whether or not it can entirely replace routine microbiology depends on several conditions and future developments, both technological and computational (see \secref{sec:bioinformatics}).

\begin{figure*}[h!]
\centering
\includegraphics[width=\textwidth]{figures/introduction/Figure 4.pdf}
\caption{\textbf{Hypothetical workflow based on metagenomic sequencing.} Schematic representation of the hypothetical workflow for the direct processing of samples from suspected sources of pathogens after adoption of metagenomic sequencing, with an expected timescale that could fit within a single day. Adapted from \cite{didelot_transforming_2012}}
\label{fig:figure4}
\end{figure*}
